\section{Introduction}

Talk about motivation, contribution and outline paper 

\todo[inline]{Perhaps we can talk about how current developers debug
  their systems in UAV software}

\section{Background / Related Work}

\todo[inline]{Setting the stage, what is the landscape like? Where has
  been done and where are the gaps? }

\subsection{Faults / Bugs}
\subsubsection{Aerospace / NASA}
\subsubsection{Computer Science}

\subsection{Fault Detection}
\subsubsection{Aerospace / NASA}
\subsubsection{Computer Science}

\section{Example Walkthrough}
In CS papers, this is similar to where the author walks the
reader through the system using a simple example.

\todo[inline]{Does it make sense to include this section?}

\section{Proposed Bug-Detection Algorithm}

\subsection{Overview}

Two-phase process

\subsection{Buffering}

Variables monitored here will be slightly different from AIAA paper

\subsection{Feature Extraction}

8 features

\subsection{Clustering Assignment}

\subsection{Fault Probability Model}


\section{Experimental Setup}

\subsection{Simulation Software}

This will be significantly different as we are moving to
Ardupilot. 

\subsection{Continous Descent and Missed Approach Scenarios}

\subsection{Fault Injection Scenarios}

\todo[inline]{What kind of bugs are you looking at here? What is the
  justification for looking at these bugs versus other kinds of bugs?}

Injecting one bug at a time for now

\begin{enumerate}
\item Units bug from AIAA paper
\item Three more bugs
\end{enumerate}

\subsection{Data Collection}

Talk about experimental setup. Significant updates here


\section{Model Training}

\todo[inline]{This section always sticks out, doesn't quite fit
  any where else}

\section{Evaluation}

\todo[inline]{How does this compare with the current state of the
  art?}

\subsection{Detection Accuracy}

\todo[inline]{How well does it detect bugs? ROC curves}

\section{Discussion of Current Limitations}

\todo[inline]{Where does it fail?}

Some questions we have not answered:

\todo[inline]{What is the overhead on the application?}
\todo[inline]{What is the average time to detection from onset of fault?}

\section{Conclusion}

\section{Acknowledgement}
