\section{Problem Description}  \label{sec:physys}

%% Description of the problem you are trying to solve and the states you
%% are trying to control; description of the performance goal(s) you seek
%% to achieve through controller/estimator design.

\subsection{System Description}

The system that I am looking at is a software system, specifically
looking at trying to apply state estimation ideas to software. The
particular problem I am examining is insertion sort.

\begin{description}
\item[State] The state is the list of numbers to be sorted.
\item[Sensor Model] The hardest part of this project is coming up with a
  sensor model. Currently I am assuming perfect sensing into random
  elements of the sorted portion of the list.
\item[Prediction] State estimation methods such as the Kalman Filter
  generates a prior based on model dynamics, usually denoted $
  \hat{\mathbf{x}}_{k}^{+}$. For insertion sort, we will initially
  assume that the estimator is estimating the location to insert a new item
  in the sorted list. To produce this estimate, we will use the lever
  rule:
  \begin{align}
    f &= \frac{newval - lowval}{highval - lowval} \\
    i\_est &= (i\_high - i\_low)*f + i\_low
  \end{align}  
\item[Correction] To produce $\hat{\mathbf{x}}_{k}^{-}$, we are
  currently exploring two options. The first option is to use the
  sensor values and the ground truth and generate a residual, then we
  can use the residual to sort locally the place where the residual
  occurred. The second option is to do the lever rule again.
\end{description}

\subsection{Performance Goals} \label{subsec:perfgoals}

%% There are two performance goals that I am interested in. The optimatl
%% estimator shall:
%% \begin{description}
%% \item [A] Have an average absolute error that is less than 10 fee in
%%   its estimate of current altitude. 
%% \item [B] Be able to complete the estimation within 0.01 second.
%% \end{description}
